\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
removed negative -2001 .. -2007 fictitious CPML materials, which are now unused.

\item [materials\_file] Contains the material associations for each element. The format is:
\begin{lyxcode}
\texttt{element\_ID} \texttt{material\_ID}
\end{lyxcode}
where \texttt{element\_ID} is the element identifier and \texttt{material\_ID} is a unique identifier, positive (for materials) or negative (for tomographic models or C-PML elements).
For C-PML absorbing conditions, \texttt{material\_ID} is a unique negative identifier between -2001 and -2007 in correspondance to the convention seen above in the description of the
absorbing\_cpml\_file: -2001 <-> 1, -2002 <-> 2, etc\ldots

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For fully defined materials, the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.

\item For C-PML absorbing conditions, , the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier between -2001 and -2007 to correspond with the definition given in materials\_file,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
%For a tomographic model, the material definition format is:
%\begin{lyxcode}
%\texttt{domain\_ID} \texttt{material\_ID}  \texttt{tomography}  \texttt{name}
%\end{lyxcode}
%where
%\texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a negative, unique identifier, \texttt{tomography} keyword for tomographic material definition and \texttt{name} the name of the tomography file. The name is not used so far, rather change the filename defined in the file \texttt{model\_tomography.f90} located in the
%\texttt{src/generate\_databases/} directory.
%
\end{itemize}

>>>>

\item [materials\_file] Contains the material associations for each element. The format is:
\begin{lyxcode}
\texttt{element\_ID} \texttt{material\_ID}
\end{lyxcode}
where \texttt{element\_ID} is the element identifier and \texttt{material\_ID} is a unique identifier,
positive (for materials taken from this list of materials, i.e. for which each spectral
element has constant material properties taken from this list) or negative (for tomographic models,
i.e. for spectral element whose real velocities and density will be assigned later by calling an external function
to define model variations, for instance in the case of tomographic models; in such a case, material properties
can vary inside each spectral element, i.e. be different at each of its Gauss-Lobatto-Legendre grid points).

\item [nummaterial\_velocity\_file] Defines the material properties.
\begin{itemize}
\item For classical materials (i.e., spectral elements for which the velocity and density
model will not be assigned by calling an external function to define for instance a tomographic model), the format is:
\begin{lyxcode}
\texttt{domain\_ID} \texttt{material\_ID}  \texttt{rho}  \texttt{vp}  \texttt{vs}  \texttt{Q}  \texttt{anisotropy\_flag}
\end{lyxcode}
where \texttt{domain\_ID} is 1 for acoustic or 2 for elastic materials, \texttt{material\_ID} a unique identifier,  \texttt{rho} the density in $kg \, m^{-3}$,  \texttt{vp} the P-wave speed in $m \, s^{-1}$, \texttt{vs}  the S-wave speed in $m \, s^{-1}$, \texttt{Q} the quality factor and \texttt{anisotropy\_flag} an identifier for anisotropic models.
%%magnoni
\item For tomographic velocity models, please read Chapter \ref{cha:-Changing-the} and Section \ref{sec:Using-tomographic} `Using external tomographic Earth models' for further details.
%
\end{itemize}
